Scheeper's Meager-NWD Game and the Menger Game

### 2015-02-04 phd/dissertation/chapter2.tex
tweaks based on meeting with Rodger

\begin{defn}
  A \term{game} is a tuple $\<M,W\>$ such that
  $W\subseteq M^{\omega}$. $M$ is the set of \term{moves} for
  the game, and $M^{\omega}$ is the set of all possible
  \term{playthroughs} of the game.

  $W$ is the set of \term{winning playthroughs} or \term{victories} for the
  first player, and $M^{\omega}\setminus W$ is the set of victories for the
  second player. ($W$ is often called the \term{payoff set} for the
  first player.)
\end{defn}

@@

Intuitively, a strategy is a rule for one of the players on how to play
the game based upon the previous (finite) moves of the opponent, while an
attack is a fixed strike by an opponent indexed by round number.

@@

If we wish to show that a winning strategy does not exist for a player
(i.e. $\pl A\notwin G$), we
often consider an arbitrary legal strategy, and use it to define a legal
\term{counter-attack} for the opponent. If we can prove that the result of
the game for that strategy and counter-attack is a victory for the opponent,
then a winning strategy does not exist.

Unlike finite games, is not the case that a winning strategy must exist for
one of the players in an infinite game.

>>>>

\begin{defn}
  A \term{game} is a tuple $\<M,W\>$ such that
  $W\subseteq M^{\omega}$. $M$ is the set of \term{moves} for
  the game, and $M^{\omega}$ is the set of all possible
  \term{playthroughs} of the game.
  $W$ is the set of \term{winning playthroughs} or \term{victories} for the
  first player, and $M^{\omega}\setminus W$ is the set of victories for the
  second player. ($W$ is often called the \term{payoff set} for the
  first player.)
\end{defn}

@@

Intuitively, a strategy is a rule for one of the players on how to play
the game based upon the previous (finite) moves of the opponent, while an
attack is a fixed sequence of moves determined by the opponent before
the game begins.

@@

If we wish to show that a winning strategy does not exist for a player
(i.e. $\pl A\notwin G$), we
often consider an arbitrary legal strategy, and use it to define a legal
\term{counter-attack} for the opponent. If we can prove that the result of
the game for that strategy and counter-attack is a victory for the opponent,
then a winning strategy does not exist for that player.

Unlike finite games, it is not the case that a winning strategy must exist for
one of the players in an infinite game.
